FTLR proof cases

### 2018-03-13 fully-abstract-comp/ftlr-proof-cases.tex
Add a note, fix typo.

\begin{lemma}[non-linear words are pure]
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
  \dominique{11-3-2018: proving this lemma depends on lemma~\ref{lem:world-fut-purePart} for the higher-order cases.}
\end{lemma}

\begin{lemma}[load from capability works]
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $\npair{(c,c)}\in\lrv(H_\sigma,W)$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \item $w_S = \linCons{\ms_S(a)}$, $w_T = \linCons{\ms_T(a)}$
  \item $\linConsPerm{\perm}$
  \end{itemize}
  Then $\exists W', W_M'\ldotp$
  Additionally, if
  \begin{itemize}
  \item $W_M = W' \oplus W_M'$
  \item $\memSat{(\ms_S\update{\mem.a}{w_S},\stk,\ms_\stk,\ms_T\update{\mem.a}{w_T})}{W_M'}$
  \item $\npair{(\ms_S(a),\ms_T(a))} \in \lrv(W')$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

>>>>

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
  \dominique{11-3-2018: proving this lemma depends on lemma~\ref{lem:world-fut-purePart} for the higher-order cases.}
\end{lemma}

\begin{lemma}[load from capability works]
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $c = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
  \item $\npair{(c,c)}\in\lrv(H_\sigma,W)$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \item $w_S = \linCons{\ms_S(a)}$, $w_T = \linCons{\ms_T(a)}$
  \item $\linConsPerm{\perm}$
  \end{itemize}
  Then $\exists W', W_M'\ldotp$
  \begin{itemize}
  \item $W_M = W' \oplus W_M'$
  \item $\memSat{(\ms_S\update{\mem.a}{w_S},\stk,\ms_\stk,\ms_T\update{\mem.a}{w_T})}{W_M'}$
  \item $\npair{(\ms_S(a),\ms_T(a))} \in \lrv(W')$
  \end{itemize}
  \dominique{11-3-2018: this lemma depends on Lemma~\ref{lem:non-linear-pure} for the non-linear case.}
\end{lemma}
\begin{proof}
  TODO
\end{proof}
